### 2012-11-26 inst/examples/mult_uncertainty_test.Rmd
transparent plots

```{r plotting, include=FALSE}
opts_knit$set(upload.fun = socialR::notebook.url)
opts_chunk$set(dev.args=list(bg="transparent"))
```

@@

    # Much faster to fill out f calls as a matrix ahead of time.  
    f_matrix <- outer(x_grid, h_grid, f, p)

    F <- lapply(1:n_h, function(q){  
      t(sapply(1:n_x, function(y){
        out <- numeric(n_x)
        mu <- M[y,] %*% f_matrix %*% I[q,] 
        # Handle special cases
        if(snap_to_grid(mu,x_grid)==0){ # 
          out[1] <- 1   
        } else {
         # snap mu to grid first?  then do this by table look-up?
         out <- pdfn(x_grid, mu, sigma_g)  ## All computational time spent here.  could be done by look-up?
        }
        out/sum(out)
      }))
    })

    # n_y by n_x, given y %*% n_x by n_h %*% n_h by n_q, given q
    Ep <- M %*% P %*% t(I)
    V <- Ep
    for(t in 1:Tmax){
      D[,(Tmax-t+1)] <- apply(V, 1, which.max) 
      ## q can often exceed y, if fishing is free, there might be more x than you think.  
      #if(any(pmin(D[,(Tmax-t+1)], 1:n_h) !=  D[,(Tmax-t+1)])) stop()
      #v_t <- sapply(1:n_h, function(i) V[i,D[i,(Tmax-t+1)]]) # Look-up value given by which.max
      v_t <- apply(V, 1, max) # vector of current values 
      V <- sapply(1:n_h, function(j){ # updated value matrix
        Ep[,j] + (1-delta) * M %*% F[[j]] %*% v_t
      })
    }
    list(D=D, M=M, I=I, P=P, Ep=Ep, V=V, F=F)
}

@@

pars <- c(1.5, 0.05)
K <- (pars[1] - 1)/pars[2]
xmin <- 0
xmax <- 1.5 * K
n_x <- 200
n_h <- n_x
x_grid <- seq(xmin, xmax, length = n_x)  
h_grid <- seq(xmin, xmax, length = n_h)
delta <- 0.05
xT <- 0
OptTime <- 25

@@

```{r noisetypes}
g <- SDP_multiple_uncertainty(f, pars, x_grid, h_grid, OptTime, sigmas = c(sigma_g=sigma_g, sigma_m=0, sigma_i=0), pdfn=pdfn)  
m <- SDP_multiple_uncertainty(f, pars, x_grid, h_grid, OptTime, sigmas = c(sigma_g=0.03, sigma_m=0.3, sigma_i=0), pdfn=pdfn)  
i <- SDP_multiple_uncertainty(f, pars, x_grid, h_grid, OptTime, sigmas = c(sigma_g=0.03, sigma_m=0, sigma_i=0.3), pdfn=pdfn)  
```

>>>>

```{r plotting, include=FALSE}
opts_knit$set(upload.fun = socialR::notebook.url)
opts_chunk$set(dev.args=list(bg="transparent"))
theme_update(plot.background = element_rect(fill = "transparent",colour = NA))
```

@@

    # Much faster to fill out f calls as a matrix ahead of time.  
    f_matrix <- outer(x_grid, h_grid, f, p)
    # Fill out uncertainty in transitions first
    G <- outer(x_grid, x_grid, pdfn, sigma_g)

    F <- lapply(1:n_h, function(q){  
      t(sapply(1:n_x, function(y){
        out <- numeric(n_x)
        mu <- M[y,] %*% f_matrix %*% I[q,] 
        # Handle special cases
        if(snap_to_grid(mu,x_grid)==0){ # 
          out[1] <- 1   
        } else {
        #out <- pdfn(x_grid, mu, sigma_g)  ## All computational time spent here.  could be done by look-up:
         mu_i <- which.min(abs(x_grid - mu)) ## snap mu to grid first
         out <- G[,mu_i]   ## then do this by table look-up
         ## Not identical but very close.  
        }
        out/sum(out)
      }))
    })

    # n_y by n_x, given y %*% n_x by n_h %*% n_h by n_q, given q
    Ep <- M %*% P %*% t(I)
    V <- Ep
    for(t in 1:Tmax){
      D[,(Tmax-t+1)] <- apply(V, 1, which.max) 
      ## q can often exceed y: if fishing is free, there might be more x than you think.  
      #if(any(pmin(D[,(Tmax-t+1)], 1:n_h) !=  D[,(Tmax-t+1)])) stop()
      #v_t <- sapply(1:n_h, function(i) V[i,D[i,(Tmax-t+1)]]) # Look-up value given by which.max
      v_t <- apply(V, 1, max) # vector of current values 
      V <- sapply(1:n_h, function(j){ # updated value matrix
        Ep[,j] + (1-delta) * M %*% F[[j]] %*% v_t
      })
    }
    list(D=D, M=M, I=I, P=P, Ep=Ep, V=V, F=F)
}

@@

pars <- c(1.5, 0.05)
K <- (pars[1] - 1)/pars[2]
xmin <- 0
xmax <- 1.5 * K
n_x <- 150
n_h <- n_x
x_grid <- seq(xmin, xmax, length = n_x)  
h_grid <- seq(xmin, xmax, length = n_h)
delta <- 0.05
xT <- 0
OptTime <- 25

@@

```{r }
g <- SDP_multiple_uncertainty(f, pars, x_grid, h_grid, OptTime, sigmas = c(sigma_g=sigma_g, sigma_m=0, sigma_i=0), pdfn=pdfn)
```

```{r}
m <- SDP_multiple_uncertainty(f, pars, x_grid, h_grid, OptTime, sigmas = c(sigma_g=0.03, sigma_m=0.3, sigma_i=0), pdfn=pdfn)  
```

```{r}
i <- SDP_multiple_uncertainty(f, pars, x_grid, h_grid, OptTime, sigmas = c(sigma_g=0.03, sigma_m=0, sigma_i=0.3), pdfn=pdfn)  
```
